---
title: "Homework 1"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

#### Create a 5 by 10 matrix of random integers
```{r}
m <- matrix(sample.int(100,size=50),nrow=5,ncol=10)
```

#### Define column names as cond1, cond2, cond3, cond4, cond5, ctrl1, ctrl2, ctrl3, ctrl4, ctrl5
```{r}
cnames <- c("cond1", "cond2", "cond3", "cond4", "cond5",
           "ctrl1", "ctrl2", "ctrl3", "ctrl4", "ctrl5")
colnames(m) <- cnames
```

#### Define row names as gene1, gene2, gene3 ...
```{r}
rnames <- c("gene1", "gene2", "gene3", "gene4", "gene5")
rownames(m) <- rnames
```

#### Compute the fold change for each gene.

__*A question regarding calculating the fold change for each gene:*__ 

In our matrix, we have two groups, "cond" and "ctrl", and each group has 5 samples. If we are to calculate fold change, should we calculate it as "cond1" vs "ctrl1", "cond2" vs "ctrl2" etc, or should we use the method in DESeq2 package, where they use some term called "pseudo-reference counts" to normalize the samples in each group, then calculate the lo2FC overall?

```{r}
coldata <- data.frame(genes = rnames,
                      conditions = cnames)
coldata$conditions <- factor(substr(cnames, start = 1, 
                                    stop = nchar(cnames[1]) - 1))
dds <- DESeq2::DESeqDataSetFromMatrix(countData = m,
                                      colData = coldata,
                                      design = ~ conditions)
dds$conditions <- factor(dds$conditions, levels = c("cond","ctrl"))
dds <- DESeq2::DESeq(dds)

# Calculate log2FoldChange of control vs condition
res <- DESeq2::results(dds, contrast=c("conditions","cond","ctrl"))
res
```





