---
title: "My First Notebook"
output: html_notebook
---

library() - opens a window listing the downloaded packages
```{r}
library()
```

search() - shows which ones are currently loaded.
```{r}
search()
```

Help page for vignette function
```{r}
?vignette
```


```{r}
# to get help on using install.packages
?install.packages

# Note: the parameter is a quoted string!
if (! requireNamespace("seqinr", quietly=TRUE)) {
  install.packages("seqinr")
}
```

Launch seqinr package info
```{r}
library(help="seqinr") 
```


List all the functions available in the seqinr package.
```{r}
#Note: the file must be attached in order for the below function to work 
library(seqinr)
ls("package:seqinr")
```

Help page for function "a" in seqinr
```{r}
?seqinr::a 
```


Run the fiction to see the output
```{r}
seqinr::a("Tyr")
```

What does function below do? Include in journal
```{r}
seqinr::words(3, c("A", "G", "C", "U"))
# This function generates the all words from the given alphabet with given length. In this example, our alphabet is AGCU, and the length is 3, so we can generate all combination of codons.

?seqinr::words # Check the help page
```

Load all data sets available in R
```{r}
?data
```

Load datasets available in seqinr
```{r}
data(package="seqinr") 
  
```


The aaindex dataset in the package
```{r}
data(aaindex, package="seqinr") 
```

Two indices
```{r}
aaindex$FASG890101 
```

```{r}
aaindex$PONJ960101 
```

Plot amino acid single-letter codes by hydrophobicity and volume.
```{r}
plot(aaindex$FASG890101$I,
     aaindex$PONJ960101$I,
     xlab="hydrophobicity", ylab="volume", type="n")
text(aaindex$FASG890101$I,
     aaindex$PONJ960101$I,
     labels=a(names(aaindex$FASG890101$I)))
```

```{r}
seqinr::choosebank("swissprot")
mySeq <- seqinr::query("mySeq", "N=MBP1_YEAST")
mbp1 <- seqinr::getSequence(mySeq)
seqinr::closebank()
x <- seqinr::AAstat(mbp1[[1]])
barplot(sort(x$Compo), cex.names = 0.6)
```


Load the package
```{r}
library(seqinr)
choosebank("swissprot")
mySeq <- query("mySeq", "N=MBP1_YEAST")
mbp1 <- getSequence(mySeq)
closebank()
x <- AAstat(mbp1[[1]])
barplot(sort(x$Compo), cex.names = 0.6)
```

Get package information with the following:
```{r}
library(help = seqinr)
browseVignettes("seqinr")
data(package = "seqinr")
```


Look for a package
```{r}
if (! requireNamespace("sos", quietly=TRUE)) {
    install.packages("sos")
}
library(help = sos)       # basic information
browseVignettes("sos")    # available vignettes
 
sos::findFn("moving average")
```


```{r}
5
5 + 3
5 + 1 / 2 # Think first: is this 3 or 5.5
3 * 2 + 1
3 * (2 + 1)
2^3 # Exponentiation
8 ^ (1/3) # Third root via exponentiation
7 %% 2  # Modulo operation (remainder of integer division)
7 %/% 2 # Integer division

# Logical operators return TRUE or FALSE
#    Unary:
TRUE
FALSE
! TRUE  # read carefully: the "!" (meaning "not") is easily overlooked
! FALSE
 
#    Binary operators
 
1 == 2
1 != 2
1 < 2
1 > 2
 
1 > 1
1 >= 1
1 < 1
1 <= 1
 
#    & (means AND)
TRUE & TRUE
TRUE & FALSE
FALSE & FALSE
 
#    | (means OR)
TRUE | TRUE
TRUE | FALSE
FALSE | FALSE
 
# Predict what this will return
!(FALSE | (! FALSE))
```

Don't use the same variable name as the parameter name.
Bad example below:
```{r}
# I don't like...
col <- c("red", "grey")
hist(rnorm(200), col=col) # Don't use col=col!!
```

Good example below:
```{r}
# I prefer instead something like...
stripes <- c("red", "grey")
hist(rnorm(200), col=stripes)
```